---
title: "Case2"
author: "Julia"
date: "2023-11-14"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
library(stringr)

load("./data_2.RData")
```

1. Calculate and record the annualized mean net of the risk-free rate, annualized standard deviation, and annualized Sharpe Ratio of returns for each trading strategy except BRK-A

```{r}
#New trading strategy
nts = dt1[,1:5]
kts = dt1[,6:9] #known trading strategy
rf = dt1[,10]

#Mean of nts
nts.mean = colMeans(nts - rf) * 12

#SD of nts
nts.sd = apply(nts, 2, sd) * 12^0.5

#Sharpe 
nts.sr = nts.mean / nts.sd

q1 = as.data.frame(cbind(nts.mean,nts.sd,nts.sr))
q1
```


2. Calculate and record the regression results for a one factor model where the only factor is RM-Rf. Please report the alpha (as a percentage), the beta (as a number), the R-squared (as a number) of the regression, and the t stats (coefficient/standard error) for the alpha and beta (as numbers). For each strategy compute the idiosyncratic (diversifiable) variance and market (non-diversifiable, systematic) variance as percentages of the total variance. Perform this for each trading strategy except BRK-A.
```{r}
reg_capm = NULL

nts.names = colnames(nts)
for(nts.name in nts.names) {
  lm.temp = lm(unlist(nts[nts.name] - rf) ~ kts$Mkt.RF)
  sum = summary(lm.temp)
  ab = sum$coefficients[, "Estimate"]
  ab.se = sum$coefficients[, "Std. Error"]
  R = sum$r.squared
  ab.h0 = c(0,1)
  ab.tstat = (ab - ab.h0) / ab.se
  reg = c(ab, R, ab.tstat)
  reg_capm = rbind(reg_capm, reg)
}
#All have significant alpha's but it is not clear if that is due to mispricing or
#another set of factors that have not been accounted for
reg
reg_capm[1,4:5] = NA
rownames(reg_capm) = nts.names
colnames(reg_capm) = c("alpha", "beta", "R-squared", "tstat.alpha", "tstat.beta")
reg_capm = as.data.frame(reg_capm)
reg_capm$alpha = paste0(round(reg_capm$alpha * 100, 3), '%')
reg_capm

sys = reg_capm$'R-squared'
idio = 1 - sys
var = data.frame(nts.mean, nts.sd, nts.sr, sys, idio)
var
```


3. Calculate and record the regression results for a four factor model where the factors are RM-Rf, SMB, HML, and MOM (as labeled on the data sheet). Please report the alpha (as a percentage), the beta on each factor (as a number), the R-squared (as a number) of the regression, and the t stats (coefficient/standard error) for the alpha and betas (as numbers). Perform this for each trading strategy except BRK-A.
```{r}
reg_4fac = NULL

for(nts.name in nts.names) {
  lm.temp = lm(unlist(nts[nts.name] - rf) ~ kts$Mkt.RF + kts$SMB + kts$HML + kts$MOM)
  sum = summary(lm.temp)
  coef = sum$coefficients[, "Estimate"]
  coef.se = sum$coefficients[, "Std. Error"]
  R = sum$r.squared
  coef.h0 = c(0,1,0,0,0)
  coef.tstat = (coef - coef.h0) / coef.se
  reg = c(coef, R, coef.tstat)
  reg_4fac = rbind(reg_4fac, reg)
}

reg_4fac[, 2:5] = round(reg_4fac[, 2:5], 3)
reg_4fac[, 6:11] = round(reg_4fac[, 6:11], 2)
reg_4fac[1, 7:11] = NA
rownames(reg_4fac) = nts.names
colnames(reg_4fac) = c('alpha', 'Mkt-RF', 'SMB', 'HML', 'MOM', 'R-Squared',
                       'tstat.alpha', 'tstat.Mkt-RF', 'tstat.SMB', 'tstat.HML', 'tstat.MOM')
reg_4fac = as.data.frame(reg_4fac)
reg_4fac$alpha = paste0(round(reg_4fac$alpha * 100, 3), '%')
reg_4fac
```


4. Calculate and record the regression results for a four factor model where the factors are RM-Rf, SMB, HML, and MOM (as labeled on the data sheet). Please report the alpha (as a percentage), the beta on each factor (as a number), the R-squared (as a number) of the regression, and the t stats (coefficient/standard error) for the alpha and betas (as numbers). Record these results for BRK-A for its full history, for the subsample beginning April 1980 and ending December 2007 and for the subsample beginning January 2008 and ending December 2013. Also record the Sharpe Ratio for BRK-A and the value weighted market index for the full 1980-2013 sample.
```{r}
reg_bkr = NULL
full = rep(TRUE, nrow(dt2))
sub1 = substr(rownames(dt2), 1,4) %in% as.character(1980:2007)
sub2 = !sub1
ind = cbind(full, sub1, sub2)
for(i in 1:ncol(ind)) {
  samp = dt2[ind[,i],]
  rf2 = samp[, 6]
  BRK = samp[, 1]
  kts2 = samp[, 2:5]
  msr = mean(kts2[,1]) / sd(kts2[, 1] + rf2)
  sr = mean(BRK - rf2) / sd(BRK)
  lm.temp = lm(BRK - rf2 ~ kts2$Mkt.RF + kts2$SMB + kts2$HML + kts2$MOM)
  sum = summary(lm.temp)
  coef = sum$coefficients[, "Estimate"]
  coef.se = sum$coefficients[, "Std. Error"]
  R = sum$r.squared
  coef.h0 = 0
  coef.tstat = (coef - coef.h0) / coef.se
  reg = c(msr, sr, coef, R, coef.tstat)
  reg_bkr = rbind(reg_bkr, reg)
}

reg_bkr = as.data.frame(reg_bkr)
rownames(reg_bkr) = c('Full', '1980-2007', '2008-2013')
colnames(reg_bkr) = c('Market Sharpe Ratio', 'Sharpe Ratio', 'alpha', 'Mkt-Rsquared', 'SMB', 'HML', 'MOM',
                      'R-squared', 'tstat.alpha', 'tstat.Mkt-RF', 'tstat.SMB', 'tstat.HML', 'tstat.MOM')
reg_bkr$alpha = paste0(round(reg_bkr$alpha * 100, 3), '%')
reg_bkr
```


5. Use the investable index returns on the “dt3” sheet (VFINX: Long Large Stocks, NAESX: Long Small Stocks, VIVAX: Long Value Stocks) to construct an appropriate long only benchmark for Berkshire Hathaway based on any criteria you find relevant and compute the active returns and the tracking error for Berkshire relative to this benchmark. Your construction procedure need not be regression based, but should be justifiable. Compute the mean active returns and tracking error over the whole sample and over the January 2008- December 2013 subsample. Read Question 4 before completing this direction, as it will provide considerations relevant to appropriate benchmark
construction.
```{r}
library(stringr)
library(Rsolnp)

y = dt3$BRK.A
x1 = dt3$Vanguard.S.P.500.Index.Inv..VFINX.
x2 = dt3$Vanguard.Small.Cap.Index.Inv..NAESX.
x3 = dt3$Vanguard.Value.Index.Inv..VIVAX.

ind_sub = str_sub(rownames(dt3), -4, -1) %in% as.character((2008:2013))

#Loss function
f_loss = function(b) {
  p = y
  b = b[1] + b[2]*x1 + b[3]*x2 + b[4]*x3
  return(sum((b-p)^2))
}

#Equality constraints function
eq = function(b) {
  return(b[2] + b[3] + b[4])
}

#Random start point
theta = c(0.1, 0.5, 0.25, 0.25)

f = function(dt, sub = FALSE, Shorts = FALSE) {
  if(sub) {
    dt = dt[ind_sub,]
  }
  y = dt[,1]
  x1 = dt[,2]
  x2 = dt[,3]
  x3 = dt[,4]
  
  #Define loss function
  f_loss = function(b) {
    p = y
    b = b[1] + b[2]*x1 + b[3]*x2 + b[4]*x3
    return(sum((b-p)^2))
  }
  if (Shorts) {
    m = solnp(theta, f_loss, eqfun = eq, eqB = 1, LB = c(-Inf, -Inf, -Inf, -Inf))
  } else {
    m = solnp(theta, f_loss, eqfun = eq, eqB = 1, LB = c(-Inf, 0,0,0))
  }
  w = m$pars
  y_b = as.matrix(dt) %%w
  mar = mean(y - y_b)
  te = sd(y - y_b)
  return(c(w, mar, te))
}

#No shorts unit exposure
r1 = f(dt3, sub = F, Shorts = F)
#Short unit exposure
r2 = f(dt3, sub = F, Shorts = T)
#Recent no shorts unit exposure
r3 = f(dt3, sub = T, Shorts = F)
#Recent short unit exposure
r4 = f(dt3, sub = T, Shorts = T)

r = as.data.frame(rbind(r1, r2, r3, r4))
rownames(r) = c('1993-2013 No shorts unit exposure', 
                '1993-2013 Shorts unit exposure',
                '2008-2013 No shorts unit exposure',
                '2008-2013 Shorts unit exposure')
colnames(r) = c('alpha', 'Large', 'Small', 'Value', 'Mean active returns', 'Tracking error')
r$alpha = paste0(round(r$alpha * 100, 3), '%')
r[,-1] =  round(r[,-1], 3)
r
```

